LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2021-11-16 src/ms.tex
fix python link
arrange figures more nicely

This can be most efficiently accomplished using \lw{}'s source class, since \lw{} can then compute the merger times and signal-to-noise ratio of each source with only two lines of code. We convert the SNRs to horizon distances using Eq.~\ref{eq:snr_to_hor_dist} and plot the result in Figure~\ref{fig:horizon_distance}. The shape of the LISA sensitivity curve is clearly reflected in the horizon distance. This is because circular sources only emit at a single frequency and thus every feature in the sensitivity curve has a strong effect on the SNR (and therefore horizon distance) for circular sources. We also see that once the merger time of a source is shorter than the LISA mission length (shown by the black dotted line), the horizon distance sharply decreases. This is because if a source merges before the LISA mission concludes, it has less time to accumulate signal and thus has a lower SNR and horizon distance.

@@

@@

Let's consider a binary with the following initial parameters
\begin{align*}
    m_1 &= m_2 = 15 \unit{M_{\odot}},\ d = 20 \unit{kpc},\\
    f_{\rm orb, i} &= 3 \times 10^{-5} \unit{Hz},\ e_i = 0.5,
\end{align*}
and use \lw{} to evolve the system until 100 years before its merger with 1000 linearly spaced timesteps, recording the eccentricity and frequency at each timestep.

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{figures/detector_sc_compare.pdf}
    \caption{The strain spectral density of the LISA detector with different specifications \citep{Robson+2019} and the TianQin detector \citep{Huang+2020}. We show the LISA curve for three different mission lengths and once with an approximate response function.}
    \label{fig:detector_sc_compare}
\end{figure}

@@

\software{\lw{} is written in \texttt{Python}, available from \url{python.org}. We make use of the following Python packages: \texttt{matplotlib} \citep{Hunter+2007}, \texttt{NumPy} \citep{2020NumPy-Array},
\texttt{Astropy} \citep[\url{http://www.astropy.org}][]{AstropyCollaboration+2013,AstropyCollaboration+2018}, \texttt{Seaborn} \citep{Waskom+2021}, \texttt{SciPy} \citep{2020SciPy-NMeth}, \texttt{Numba} \citep{numba} and \texttt{Schwimmbad} \citep{Price-Whelan+2017}.}

>>>>

This can be most efficiently accomplished using \lw{}'s \href{https://legwork.readthedocs.io/en/latest/api/legwork.source.Source}{\color{\lwColour}{\texttt{Source}}} class, since \lw{} can then compute the merger times and signal-to-noise ratio of each source with only two lines of code. We convert the SNRs to horizon distances using Eq.~\ref{eq:snr_to_hor_dist} and plot the result in Figure~\ref{fig:horizon_distance}. The shape of the LISA sensitivity curve is clearly reflected in the horizon distance. This is because circular sources only emit at a single frequency and thus every feature in the sensitivity curve has a strong effect on the SNR (and therefore horizon distance) for circular sources. We also see that once the merger time of a source is shorter than the LISA mission length (shown by the black dotted line), the horizon distance sharply decreases. This is because if a source merges before the LISA mission concludes, it has less time to accumulate signal and thus has a lower SNR and horizon distance.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{figures/detector_sc_compare.pdf}
    \caption{The strain spectral density of the LISA detector with different specifications \citep{Robson+2019} and the TianQin detector \citep{Huang+2020}. We show the LISA curve for three different mission lengths and once with an approximate response function.}
    \label{fig:detector_sc_compare}
\end{figure}

@@

Let's consider a binary with the following initial parameters
\begin{align*}
    m_1 &= m_2 = 15 \unit{M_{\odot}},\ d = 20 \unit{kpc},\\
    f_{\rm orb, i} &= 3 \times 10^{-5} \unit{Hz},\ e_i = 0.5,
\end{align*}
and use \lw{}'s \lwModLink{evol} module to evolve the system until 100 years before its merger with 1000 linearly spaced timesteps, recording the eccentricity and frequency at each timestep.

@@

@@

\software{\lw{} is written in \texttt{Python}, available from \url{https://www.python.org}. We make use of the following Python packages: \texttt{matplotlib} \citep{Hunter+2007}, \texttt{NumPy} \citep{2020NumPy-Array},
\texttt{Astropy} \citep[\url{http://www.astropy.org}][]{AstropyCollaboration+2013,AstropyCollaboration+2018}, \texttt{Seaborn} \citep{Waskom+2021}, \texttt{SciPy} \citep{2020SciPy-NMeth}, \texttt{Numba} \citep{numba} and \texttt{Schwimmbad} \citep{Price-Whelan+2017}.}
